---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

__Disclaimer: this repo is just a Proof of Concept and should not be used.__

# cyphersugar

{cyphersugar} is intended to bring syntactic sugar to Neo4J cypher langugage, so you can write cypher queries in a more natural way if you come from R. 

## Convention

Every cypher function is in uppercase (`MATCH`, `RETURN`, `LIMIT`...). The wrappers are in lower case (`node`, `to`, `from`...)

## Example

```{r example}
library(cyphersugar)
MATCH() %>%
  node(n = "Person", labels = c(name = "Colin")) %>%
  to(k = "KNOWS") %>%
  node("Person") %>%
  RETURN(person = "n", knows = "k") %>%
  LIMIT(25)
```

The end idea is, of course, to be able to use it with `neo4r`, or other Neo4J R Drivers.

```{r eval = FALSE}
library(neo4r)
con <- neo4j_api$new(url = "http://localhost:7474", 
                     user = "neo4j", password = "neo4j")
con$ping()

MATCH() %>%
  node('n') %>%
  RETURN(node = "n") %>%
  LIMIT(25) %>%
  call_api(con)
```

## Examples

```{r}
CREATE(node(adam = "User", labels = c(name = "Adam")), 
       node(pernilla = "User", labels = c(name = "pernilla")), 
       node(david = "User", labels = c(name = "david")))
```

```{r}
MATCH() %>%
  node(r = "record") %>%
  to("WAS_RECORDED") %>% 
  node(b = "Band") %>% 
  RETURN("r AS band")
```

